Against the Planetary Interpretation of PTFO$\,$8-8695b

### 2020-04-15 paper/ms.tex
update paper

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf TESS lightcurve of \ptfo\ (Sector 6, Orbit 19).}
		{\it Top}: ``Raw'' \texttt{PDCSAP} mean-subtracted relative flux
		versus time. The beat period of 4.48 days is visible by eye.  The
		model plotted underneath the data includes 2 harmonics at the long
		period $P_{\rm \ell}$, plus 2 harmonics and a transit at the short
		period $P_{\rm s}$.
		{\it Upper middle}: Long-period signal, equal to the raw signal
		minus the short-period signal.
		{\it Lower middle}: Short-period signal, equal to the raw signal
		minus the long-period signal.
		{\it Bottom}: residual.  The data are binned from 2 to 10 minute
		cadence as a convenience for plotting and fitting.
		\label{fig:splitsignal}
	}
\end{figure*}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.95\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Phase-folded long and short-period signals.}
		{\it Top}: Long-period signal, as in Figure~\ref{fig:splitsignal}.
		{\it Bottom}: Short-period signal. The reference phase is set to the
		``planetary'' dip.  Gray points are the 10 minute cadence
		\texttt{PDCSAP} flux.  Black points are binned to 100 points per
		period.
		\label{fig:phasefold}
	}
\end{figure*}

@@

@@

% \begin{figure*}[t]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=0.9\textwidth]{f6.png}
% 	\end{center}
% 	\vspace{-0.7cm}
% 	\caption{ {\bf Positions, kinematics, and HR diagram of \ptfo.}
%   Members of the 25$\,$Ori-1 subgroup are shown with black circles,
%   and were identified by \citet{kounkel_apogee2_2018} through
%   clustering on Gaia-DR2 and APOGEE data.  The ``neighborhood'' (gray
%   circles) is defined as the group of at most $10^4$ randomly selected
%   non-member stars within 5 standard deviations of the mean right
%   ascension, declination, and parallax.
% 	\label{fig:gaia}
% 	}
% \end{figure*}
\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf HR diagram of \ptfo and members of 25$\,$Ori-1.}
  Members of the 25$\,$Ori-1 group (black circles) were identified by
  \citet{kounkel_apogee2_2018} by clustering on six-dimensional
  Gaia-DR2 and APOGEE-2 data.  We defined the reference
  ``neighborhood'' (gray circles) as the group of at most $10^4$
  randomly selected non-member stars within 5 standard deviations of
  the mean 25$\,$Ori-1 right ascension, declination, and parallax.
	\label{fig:gaia}
	}
\end{figure*}

>>>>

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf TESS lightcurve of \ptfo\ (Sector 6, Orbit 19).}
		{\it Top}: ``Raw'' \texttt{PDCSAP} mean-subtracted relative flux
		versus time. The beat period of 4.48 days is visible by eye.  The
		preferred model plotted underneath the data includes 2 harmonics at the long
		period $P_{\rm \ell}$, plus 2 harmonics and a transit at the short
		period $P_{\rm s}$.
		{\it Upper middle}: Long-period signal, equal to the raw signal
		minus the short-period signal.
		{\it Lower middle}: Short-period signal, equal to the raw signal
		minus the long-period signal.
		{\it Bottom}: residual.  The data are binned from 2 to 10 minute
		cadence as a convenience for plotting and fitting.
		\label{fig:splitsignal}
	}
\end{figure*}

@@

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Phase-folded long and short-period signals.}
		{\it Top}: Long-period signal, as in Figure~\ref{fig:splitsignal}.
		{\it Bottom}: Short-period signal. The reference phase is set to the
		``planetary'' dip.  Gray points are the 10 minute cadence
		\texttt{PDCSAP} flux.  Black points are binned to 100 points per
		period.
		\label{fig:phasefold}
	}
\end{figure*}

@@

% \begin{figure*}[t]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=0.9\textwidth]{f6.png}
% 	\end{center}
% 	\vspace{-0.7cm}
% 	\caption{ {\bf Positions, kinematics, and HR diagram of \ptfo.}
%   Members of the 25$\,$Ori-1 subgroup are shown with black circles,
%   and were identified by \citet{kounkel_apogee2_2018} through
%   clustering on Gaia-DR2 and APOGEE data.  The ``neighborhood'' (gray
%   circles) is defined as the group of at most $10^4$ randomly selected
%   non-member stars within 5 standard deviations of the mean right
%   ascension, declination, and parallax.
% 	\label{fig:gaia}
% 	}
% \end{figure*}
\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf HR diagram of \ptfo\ and members of 25$\,$Ori-1.}
  Members of the 25$\,$Ori-1 group (black circles) were identified by
  \citet{kounkel_apogee2_2018} through clustering on six-dimensional
  Gaia-DR2 and APOGEE-2 data.  We defined the reference
  ``neighborhood'' (gray circles) as the group of at most $10^4$
  randomly selected non-member stars within 5 standard deviations of
  the mean 25$\,$Ori-1 right ascension, declination, and parallax.
  \ptfo\ seems likely to be a photometric binary.
	\label{fig:gaia}
	}
\end{figure*}
